Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-11 write-ups/PLDI/paper.tex
Address get_global_size comment

\subsection{OpenCL Background}

@@

\paragraph{A changing number of workgroups}  Unlike in regular OpenCL,
the value returned by $\getnumgroups()$ is not fixed during the
lifetime of a cooperative kernel \TSComment{Neither is {\tt
    get\_global\_size}, is that worth mentioning?}.  Although
$\getnumgroups()$ has atomic semantics, and so can be called at any
time to yield a well-defined value, the value returned by two
successive calls may differ if workgroups have executed $\offerkill$,
$\offerfork$ or $\resizingglobalbarrier$ in-between.  The programmer
must therefore write their cooperative kernel in a manner that is
robust to changes in the value returned by $\getnumgroups()$.

@@

The situation is more stable if a cooperative kernel does not directly
issue $\offerkill$ and $\offerfork$ calls directly.  In this case,
only calls to $\resizingglobalbarrier$ can cause the number of active
workgroups to change and, as discussed in Section~\ref{sec:semantics},
this function causes synchronisation between all threads and causes
the number of active workgroups to change atomically.  At any point
during execution, the threads of a kernel are executing between some
pair of resizing barrier calls, which we call a \emph{resizing barrier
  intervals} (here we consider the kernel entry and exit points
conceptually to be special cases of resizing barriers).  The number of
workgroups executing the kernel is thus constant within each resizing
barrier interval, i.e.\ the result returned by repeated calls to
$\getnumgroups()$ will be identical during such an interval.

>>>>

\subsection{OpenCL Background}\label{sec:opencl}

@@

\paragraph{A changing number of workgroups}  Unlike in regular OpenCL,
the value returned by $\getnumgroups()$ is not fixed during the
lifetime of a cooperative kernel.  Although
$\getnumgroups()$ has atomic semantics, and so can be called at any
time to yield a well-defined value, the value returned by two
successive calls may differ if workgroups have executed $\offerkill$,
$\offerfork$ or $\resizingglobalbarrier$ in-between.  Because $\getglobalsize()$, which retrieves the total number of threads executing the kernel, is
a function of $\getnumgroups()$, the value returned by $\getglobalsize()$ is also subject to change.
The programmer
must therefore write their cooperative kernel in a manner that is
robust to changes in the values returned by these functions.

@@

The situation is more stable if a cooperative kernel does not directly
issue $\offerkill$ and $\offerfork$ calls directly.  In this case,
only calls to $\resizingglobalbarrier$ can cause the number of active
workgroups to change and, as discussed in Section~\ref{sec:semantics},
this function causes synchronisation between all threads and causes
the number of active workgroups to change atomically.  At any point
during execution, the threads of a kernel are executing between some
pair of resizing barrier calls, which we call a \emph{resizing barrier
  intervals} (here we consider the kernel entry and exit points
conceptually to be special cases of resizing barriers).  The number of
workgroups executing the kernel is thus constant within each resizing
barrier interval, i.e.\ the result returned by repeated calls to
$\getnumgroups()$ will be identical during such an interval; the same holds for $\getglobalsize()$.
